FraCaS: Temporal Analysis

### 2020-06-09 paper2020/paper.tex
some cleanup in example

\begin{verbatim}
s_279_1_p :: Phr
s_279_1_p=((sentence) ((useCl) ((past)) ((pPos)) ((predVP) ((usePN) ((lexemePN "smith_PN"))) ((advVP) ((complSlash) ((slashV2a) ((lexemeV2 "write_V2"))) ((detCN) ((detQuant) ((indefArt)) ((numSg))) ((useN) ((lexemeN "novel_N"))))) ((lexemeAdv "in_1991_Adv"))))))
s_279_3_h :: Phr
s_279_3_h=((sentence) ((useCl) ((past)) ((pPos)) ((predVP) ((usePN) ((lexemePN "smith_PN"))) ((advVP) ((complSlash) ((slashV2a) ((lexemeV2 "write_V2"))) ((usePron) ((it_Pron)))) ((lexemeAdv "in_1992_Adv"))))))
\end{verbatim}
Interpretation by our dynamic and temporal semantics:

\begin{verbatim}
Definition Problem279aFalse:= (FORALL (fun a=>novel_N a) (fun a=>(exists (b: Time), ((exists (c: Time), (IS_INTERVAL Date_19910101 b /\ IS_INTERVAL c Date_19911231 /\ IS_INTERVAL b c /\ appTime b c (write_V2 a) (PN2object smith_PN))))) -> Not (exists (f: Time), ((exists (g: Time), (IS_INTERVAL Date_19920101 f /\ IS_INTERVAL g Date_19921231 /\ IS_INTERVAL f g /\ appTime f g (write_V2 a) (PN2object smith_PN))))))).
\end{verbatim}
Unfolding definitions by Coq:

@@

\begin{verbatim}
Theorem  problem279 : Problem279aFalse.
cbv.
intros novel isSmithsNovel P1 H.
destruct P1 as [t0 [t1 [ct1 [ct2 [ct3 P1]]]]].
destruct H as [u0 [u1 [cu1 [cu2 [cu3 H]]]]].
specialize writeUnique with (x := novel)(y := SMITH) as A.
unfold UniqueActivity in A.
specialize (A _ _ _ _ P1 H) as B.
lia.
Qed.
\end{verbatim}

>>>>

{\small
\begin{verbatim}
s_279_1_p=
 sentence (useCl past pPos
  (predVP (usePN (lexemePN "smith_PN"))
          (advVP (complSlash (slashV2a (lexemeV2 "write_V2")))
                     (detCN (detQuant indefArt numSg) (useN (lexemeN "novel_N"))))
                     ((lexemeAdv "in_1991_Adv")))))
s_279_3_h=sentence (useCl past pPos (predVP (usePN (lexemePN "smith_PN")) (advVP (complSlash (slashV2a (lexemeV2 "write_V2")) (usePron it_Pron)) ((lexemeAdv "in_1992_Adv")))))
\end{verbatim}
Interpretation by our dynamic and temporal semantics:

\begin{verbatim}
FORALL (fun a=>novel_N a)
(fun a=>(exists (b: Time),
((exists (c: Time),
(IS_INTERVAL Date_19910101 b /\
 IS_INTERVAL c Date_19911231 /\
 IS_INTERVAL b c /\
 appTime b c (write_V2 a) (PN2object smith_PN))))) ->
Not (exists (f: Time),
((exists (g: Time),
 (IS_INTERVAL Date_19920101 f /\
  IS_INTERVAL g Date_19921231 /\
  IS_INTERVAL f g /\
  appTime f g (write_V2 a) (PN2object smith_PN)))))).
\end{verbatim}
Unfolding definitions by Coq:

@@

\begin{verbatim}
Theorem  problem279 : Problem279aFalse.
cbv.
intros novel isSmithsNovel P1 H.
destruct P1 as [t0 [t1 [ct1 [ct2 [ct3 P1]]]]].
destruct H as [u0 [u1 [cu1 [cu2 [cu3 H]]]]].
specialize writeUnique with (x := novel)(y := SMITH) as A.
unfold UniqueActivity in A.
specialize (A _ _ _ _ P1 H) as B.
lia.
Qed.
\end{verbatim}
}
